GEE models

### 2017-07-18 doc/esm-tables.Rmd
updated models for qic in esm-tables

- M0: log(ISSI-2) or log(ISI) = total non-esterified fatty acids (nmol/mL) + years from baseline
- M1: M0 + NEFA by time interaction
- M2: M0 + sex + ethnicity + baseline age
- M3: M2 + waist
- M4: M3 + ALT
- M5: M3 + physical activity
- M6: M3 + alcohol intake
- M7: M3 + family history of diabetes
- M8: M3 + smoking status
- M9: M3 + ALT + physical activity
- M10: M3 + NEFA by time interaction
- M11: M9 + NEFA by time interaction

>>>>

- M0: log(ISSI-2) or log(ISI) = total non-esterified fatty acids (nmol/mL) + years from baseline
- M1: M0 + NEFA by time interaction
- M2: M0 + sex + ethnicity + baseline age
- M3: M2 + waist
- M4: M3 + ALT
- M5: M3 + physical activity
- M6: M3 + alcohol intake
- M7: M3 + family history of diabetes
- M8: M3 + smoking status
- M9: M3 + ALT + physical activity
- M10: M3 + medication use for lipid and cholesterol control
- M11: M3 + NEFA by time interaction
- M12: M9 + NEFA by time interaction
